Intersection of non-matching grids of different dimensions

### 2016-09-23 paper_intersections.tex
Comments on 2d-3d.

Computation of the intersection polygon consist of three parts. In the first part (Algorithm \ref{algo:colect_23_ip_triangle}), we compute intersection points
on baundary if $S_3$ using the line-tetrahedron intersection algorithm for every side. There are 0,1, or 2 intersection points
on every side and the points are already sorted according to the side orientation, which match orientation of the intersection polygon. So, passing
through the all sides and appending the points into $I$ provides as with incomplete intersectionn polygon but in the correct order.
Then we proceed to the second part (Algorithm \ref{algo:collect_23_ip_edges}). Using the line-triangle intersection algorithm for edges of $S_4$
we obtain points from interior of $S_3$ and need to insert them into $I$ to correct place. To this end we exploit additional information about coincidence of points
with faces of $S_4$. Every point $p$ from the first part of the algorithm that is not a veertex of $S_3$ belongs to a face $f$ of $S_4$, we know from the order of the points
if the face comes before or after the point in the intersection polygon, in the first case we set $F[0,f] =p$ inthe second case we set $F[1,f]=p$. 
Every point $p$ from the second part of the algorithm lies on an edge $e$ which is between two faces $f_0$, $f_1$. The correct order of the faces on the 
intersection polygon is determined by the sign of the edge-triangle intersection. So, having the faces in the correct order we set $F[0,f_0]=p$ and $F[1, f_1]=p$.

@@

\begin{algorithm}
  \SetKw{And}{And}
  \DontPrintSemicolon
  \KwIn{input data}
  \KwOut{List of IPs sorted output data}  
  $I =\emptyset$\tcp*{Intersection polygon.}
  $F(:,:)=-1$\tcp*{Unset entries of the face connection table.}
  \For{side $s$ of $S_3$}{ 
    \nllabel{line:1_3}
    $L$ = intersection($s, S_4$)  \tcp*{List of max.\ two points.}
    process point($L[0]$, 0)\; 
    process point($L[-1]$, 1)
  }
  \lIf{ $I[0] == I[-1]$ }{remove $I[-1]$}
  \caption{2d-3d intersection, points on triangle boundary}
  \label{algo:colect_23_ip_triangle}
\end{algorithm}

\begin{algorithm}
  \SetKw{And}{And}
  \DontPrintSemicolon
  \KwIn{intersection point $p$, face relation indicator $i$}
  \KwOut{update of $I$ and $F$}
  \lIf{ $p \ne I[-1]$ }{append $p$ to $I$}
  set $j$ to index of $p$ in $I$\;
  \lIf{ $p$ is on face $f$}{ F[i,f]=j}
  \uElseIf{ $p$ is on edge $e$}{
    compute sign of intersection($e$, $S_3$)\;
    sort faces $f_0$, $f_1$ coincident with $e$\;
    F[i, $f_i$]=j
  }
  \ElseIf{ $p$ is on vertex $v$ of $S_4$}{
      \For{face $f$ coincident with $v$}{
         \lIf{ $F[i,f]==-1$}{F[i,f]=j}
      }
  }
  mark all edges of $S_4$ the $p$ lies on

  \caption{process point( $p$, $i$ )}
  \label{algo:collect_23_ip_edges}
\end{algorithm}

\begin{algorithm}
  \SetKw{And}{And}
  \DontPrintSemicolon
  \KwIn{input data}
  \KwOut{List of IPs sorted output data}  
  \For{unmarked edge $e$ of $S_4$}{
    $p$ = intersection($e, S_3$)\;
    append $p$ to $I$\;
    set $j$ to index of $p$ in $I$\;
    \uIf{ $p$ is inside of $e$}{ 
        sort faces $f_0$, $f_1$ coincident with $e$\;
        F[0, $f_0$]=j\;
        F[1, $f_1$]=j
    } %else
    \Else($p$ on the vertex $v$ of $S_4$){       
      \For{face $f$ coincident with $v$}{
         \lIf{ $F[i,f]==-1$}{F[i,f]=j}
      }
      mark all edges of $S_4$ coincident with $v$
    }
  }
  \caption{2d-3d intersection, points in triangle interior}
  \label{algo:order_23}
\end{algorithm}

\begin{algorithm}
  \SetKw{To}{To}
  \DontPrintSemicolon
  \KwIn{all points in $I$}
  \KwOut{polygon in $J$ in correct order}  
  $P=(1,\dots, n-1,0)$\tcp{array of sucessors}
  \For{ $f$ is face of $S_4$}{
    \lIf{$F[1,f] \ne F[1,f]$}{$P[ F[1,f] ] = F[0, f]$} 
  }
  $i=0$

  \lFor{$n=0$ \To $\abs{I}-1$}{
    $K[n]=I[i]$
    $i=P[i]$
  }    
  \caption{2d-3d intersection, finish sort of points}
\end{algorithm}

>>>>

Computation of the intersection polygon consists of three parts. In the first part (Algorithm \ref{algo:colect_23_ip_triangle}), we compute intersection points
on the boundary of $S_3$ using the line-tetrahedron intersection algorithm for every of its sides. There are 0,1, or 2 intersection points
on every side and the points are already sorted according to the side orientation, which match orientation of the intersection polygon. So, passing
through all the sides and appending the points into $I$ provides us with incomplete intersection polygon but in the correct order.
\notePE{Comment on process point (Algorithm \ref{algo:process_point}), face relation indicator, I would move description of face table here, since I looked at algorithm1 here, from it skipped to process point and I got lost..}

\notePE{If IP lies on an edge(s) of $S_4$, we create a mark so we exclude the edges from further computation in Algorithm \ref{algo:collect_23_ip_edges}.}

\notePE{In process point, we set for all the face of the vertex, if we coming through the vertex in or out the $S_4$. I understand that the condition on line 10 means, that we do not overwrite info if there is another IP on that face..}

\notePE{I corrected the algorithm references. Please check, it is ok now..}

Then we proceed to the second part (Algorithm \ref{algo:collect_23_ip_edges}). Using the line-triangle intersection algorithm for edges of $S_4$
we obtain points from interior of $S_3$ and need to insert them into $I$ to correct place. To this end we exploit additional information about coincidence of points
with faces of $S_4$. Every point $p$ from the first part of the algorithm \notePE{I would use proper references instead, I got confused, what 'part of algorithm' is..} that is not a vertex of $S_3$ belongs to a face $f$ of $S_4$; we know from the order of the points
whether the face comes before or after the point in the intersection polygon; in the first case we set $F[0,f] =p$, in the second case we set $F[1,f]=p$. 
Every point $p$ from the second part of the algorithm lies on an edge $e$ which is between two faces $f_0$, $f_1$. The correct order of the faces on the 
intersection polygon is determined by the sign of the edge-triangle intersection. So, having the faces in the correct order we set $F[0,f_0]=p$ and $F[1, f_1]=p$.

@@

\begin{algorithm}
  \SetKw{And}{And}
  \DontPrintSemicolon
  \KwIn{input data}
  \KwOut{List of IPs sorted output data}  
  $I =\emptyset$\tcp*{Intersection polygon.}
  $F(:,:)=-1$\tcp*{Unset entries of the face connection table.}
  \For{side $s$ of $S_3$}{ 
    \nllabel{line:1_3}
    $L$ = intersection($s, S_4$)  \tcp*{List of max.\ two points.}
    process point($L[0]$, 0)\; 
    process point($L[-1]$, 1)
    \notePE{Isn't it clearer to write the two process point lines into cycle over L?}
  }
  \lIf{ $I[0] == I[-1]$ }{remove $I[-1]$}
  \notePE{I am not sure if I understand the notation '($[-1]$)', can be explained?
The last line then checks if first and last IPs, if they are not duplicates..??}
  \caption{2d-3d intersection, points on triangle boundary}
  \label{algo:colect_23_ip_triangle}
\end{algorithm}

\begin{algorithm}
  \SetKw{And}{And}
  \DontPrintSemicolon
  \KwIn{intersection point $p$, face relation indicator $i$}
  \KwOut{update of $I$ and $F$}
  \lIf{ $p \ne I[-1]$ }{append $p$ to $I$}
  \notePE{I am missing the check whether IP is vertex of $S_3$ as referred in text.
  So what if it is a vertex?}\;
  set $j$ to index of $p$ in $I$\;
  \lIf{ $p$ is on face $f$}{ F[i,f]=j}
  \uElseIf{ $p$ is on edge $e$}{
    compute sign of intersection($e$, $S_3$)\;
    sort faces $f_0$, $f_1$ coincident with $e$\;
    F[i, $f_i$]=j
  }
  \ElseIf{ $p$ is on vertex $v$ of $S_4$}{
      \For{face $f$ coincident with $v$}{
         \lIf{ $F[i,f]==-1$}{F[i,f]=j}
      }
  }
  mark all edges of $S_4$ the $p$ lies on

  \caption{process point( $p$, $i$ )}
  \label{algo:process_point}
\end{algorithm}

\begin{algorithm}
  \SetKw{And}{And}
  \DontPrintSemicolon
  \KwIn{input data}
  \KwOut{List of IPs sorted output data}  
  \For{unmarked edge $e$ of $S_4$}{
    $p$ = intersection($e, S_3$)\;
    append $p$ to $I$\;
    set $j$ to index of $p$ in $I$\;
    \uIf{ $p$ is inside of $e$}{ 
        sort faces $f_0$, $f_1$ coincident with $e$\;
        F[0, $f_0$]=j\;
        F[1, $f_1$]=j
    } %else
    \Else($p$ on the vertex $v$ of $S_4$){       
      \For{face $f$ coincident with $v$}{
         \lIf{ $F[i,f]==-1$}{F[i,f]=j}
      }
      mark all edges of $S_4$ coincident with $v$
    }
  }
  \caption{2d-3d intersection, points in triangle interior}
  \label{algo:collect_23_ip_edges}
\end{algorithm}

\begin{algorithm}
  \SetKw{To}{To}
  \DontPrintSemicolon
  \KwIn{all points in $I$}
  \KwOut{polygon in $J$ in correct order \notePE{J should be K ?}}  
  $P=(1,\dots, n-1,0)$\tcp{array of sucessors}
  \For{ $f$ is face of $S_4$}{
    \lIf{$F[1,f] \ne F[1,f]$}{$P[ F[1,f] ] = F[0, f]$} 
    \notePE{condition should be $F[0,f] \ne F[1,f]$ ? I don't understand: successor indices should be switched?
    This way there would be same two indices..}
  }
  $i=0$

  \lFor{$n=0$ \To $\abs{I}-1$}{
    $K[n]=I[i]$
    $i=P[i]$
  }    
  \caption{2d-3d intersection, finish sort of points}
  \label{algo:order_23}
\end{algorithm}
